### 2017-06-18 src/algorithm.tex
fix errors
algo

In this section we present an FPTAS algorithm to the VPN problem.
We are given an instance of the VPN problem 
\begin{align}
D_v = (V_v, A_v)			\\
D_p = (V_p, A_p)			\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c)	\\
c
\end{align}
For now assume all values are integral and polynomial bounded in the size of the input.
Sort the DAGs topologically and assume w.l.o.g that $s_v = s_p = 1$,
$t_v = n$, and $t_p = m$.
Let $O(i, j)$ be the optimal embedding of any $1i$ virtual path, 
into a $1j$ physical path.
We can compute $O(i, j)$ as follow:
$$
O(i, j) = \min_{a \text{ ancestor of } i} \min_{b \text{ ancestor of } j} O(a, b)
+ \min_(ai, bj)
$$
Where $\min(ai, bj)$ is the optimal embedding of a virtual 
path starting at any child of $a$, $a'$ and ending at $i$ into node $j$
that respect the bottleneck constraint, i.e. $b_d(a, a') \leg bn(b, j)$.
\todo{define bn(i, j) to be the bottleneck between i and j}
We claim that $\min(ai, bj)$ can be found efficiently 
\todo{describe how}

\todo{argue about scaling and rounding}

>>>>

In this section we present an FPTAS algorithm to the \VPN problem.
We are given an instance of the \VPN problem 
\begin{align*}
D_v = (V_v, A_v)		\\
D_p = (V_p, A_p)		\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c, c)
\end{align*}
For now assume all values are integral and polynomial bounded in the size of the input.

Let $T_{v_p}(u_v, w_v, C)$ denote the minimum processing required to embed
all the virtual vertices, excluding $u_v$, on a $u_vw_v$-path into the physical
vertex $v_p$ with cost constraint $C$.
$T$ can be computed recursively as follow:
\begin{align*}
&T_{v_p}(u_v, w_v, C) = 
\min_{v_vv_v \in A_v} T_{v_p}(u_v, v_v, C - c(w_v, v_p))
\\
&T(u_v, u_v, C) = 0
\\
&T(-, -, 0) = \infty
\end{align*}

Let $O(v_v, v_p)$ denote the optimal embedding of a $s_vv_v$-path into a
$s_pv_p$-path.
Let $pi:V_v \to \N$ be any typological ordering of $V_v$. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&O(v_v, v_p) = 
\min_{\substack{
u_v : pi(u_v) < pi(v_v), 
\\
u_pv_p \in A_p
}}
O(u_v, u_p)
+
\argmin_{C : T_{v_p}(u_v, v_v, C) \leq p_c(v_p)}
\\
&O(s_v, v_p) = c(s_v, v_p)
\end{align*}

% For a physical vertex $v_p$ we define 
% $c_{v_p}(u_v, v_v):A_v \to \R = c(v_v, v_p)$.
% Given two virtual vertices $s'_v, t'_v$ and a physical vertex $v_p$, 
% one can verify that the minimum cost of embedding any 
% 
% 
% we would like to find an optimal embedding of an $s'_vt'_v$-path into
% $v_p$.
% A solution to this sub-problem can be found as follow:
% First we build the \emph{cost graph} correspond to $s'_v, t'_v$ and $v_p$, 
% the cost graph is a graph that lets us (efficiently) compute the cost of em  
% 
% For a vertex $v$ let $C(v)$ be the set of its children.
% Let $O'(s'_v, t'_v, s'_p, t'_p)$ be the optimal embedding of some virtual
% $C(s'v)t'_v$-path into the physical vertex $t'_p$ such that the bottleneck
% between $s'_p$ and $t'_p$ is at least $b_d(s'_v, t'_v)$.
% Let $c_v \in C(s'_v)$ and observe that once $c_v$ is chosen the arc 
% $(s'_v, c_v)$ determines completely whether a physical path with a feasible
% bottleneck exists, namely, 
% a physical path exists if and only if there is a physical $s'_vt'_v$-path containing only
% arcs with bandwidth at least $b_d(s'_v, c_v)$.
% On the other hand, the set of $c_vt'_v$-paths
% determine completely the cost (and processing-wise feasibility) of the embedding.
% Figure depicts the above observations.
% 
% \begin{figure}[ht]
% \centering
% \input{fig-dp}
% \caption[]{
% \begin{enumerate*}
% \item Computing $O'(s'_v, t'_v, s'_p, t'_p)$.
% \item The set of $c_dt'_v$-paths determines completely the cost of the embedding
% \item 
% The arc $(s'_v, c_d)$ determines completely the connectivity of $s'_p$ and
% $t'_p$, i.e. physical arcs with bandwidth less than $b_d(s'_v, c_d)$ can not be
% used.
% \end{enumerate*}
% }
% \end{figure}
% 
% Among all the $c_vt'_v$-paths we want to select the one that minimize the
% embedding cost under the processing capacity constraints.
% This can be done... 
% Calculating $O'(s'_v, t'_v, s'_p, t'_p)$ can be done simply by finding the
% optimal path among all children of $s'_v$.
% 
% Let $O(t'_v, t'_p)$ be the optimal embedding of some virtual $s_vt'_v$-path
% into some physical $s_pt'_p$-path then $O(t_v, t_p)$ is the global optimal
% embedding.
% Also $O(t'_v, s_p)$ can be computed efficiently for every $t'_v$ as described
% above, and $O(s_v, t'_v)$ is simply the minimum cost of embedding $s_v$ in any
% physical vertex $s'_p$ such that a physical $s'_pt'_v$-path exists.
% For an arbitrary vertices $t'_v$, and $t'_p$, $O(t'_v, t'_p)$ can be computed
% efficiently using dynamic programming with the following recursion formula:
% $$
% O(t'_v, t'_p) = 
% \min_{\substack{
% s'_v \in P(t'_v)
% \\
% s'_p \in P(t'_p)
% }}
% O(s'_v, s'_p) + O'(s'_v, t'_v, s'_p, t'_p)
% $$ 
% 
%
